A spiral galaxy's mass distribution uncovered through lensing and dynamics

### 2015-08-14 docs/results_JAMwithSB_v1.01.tex
Small changes.

\paragraph{... with Increasing Mass-to-Light Ratio Gradient.} In \S\ref{sec:results_lensing} we found from the lensing, that the light distribution might drop faster with radius than the mass distribution. This would correspond to a radially increasing total mass-to-light ratio. As velocity anisotropy alone cannot explain the observed kinematics in a simple a mass-follows-light model, we now allow for an increasing mass-to-light ratio gradient in the JAM modelling to generate a mass model from the light distribution in Table \ref{tab:MGEF814W}. We do this by assigning each of the five Gaussians in the MGE its own mass-to-light ratio and replace the total luminosity in Eq. (\ref{eq:centralItotalL}) $L_i$ with the Gaussians total Mass $M_i = \Upsilon_{i} L_i$. We treat the five $\Upsilon_i$ as free parameters and only require that $\Upsilon_{j} \geq \Upsilon_i$ when the corresponding $\sigma_j \geq \sigma_i$ to ensure an overall mass-to-light ratio that is increasing with radius. [TO DO: Discuss Figure]

@@

\begin{figure*}
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[height=6cm]{fig/jam_G_vrms.ps}
  \caption{???}
  \label{fig:???}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[height=6cm]{fig/jam_G_enclMass.ps}
  \caption{???}
  \label{fig:???}
\end{subfigure}
\caption{??? Using the surface brightness MGE for the dynamical modelling: each Gaussian got it's own M/L such that the overall M/L is increasing with radius. This is the best fit model. The enclosed mass is overplotted with Einstein mass with 4\% error (overplotted, not fitted). ??? [TO DO: nice caption]}
\label{fig:???}
\end{figure*}

>>>>

\paragraph{... with Increasing Mass-to-Light Ratio.} In \S\ref{sec:results_lensing} we found from the lensing, that the light distribution might drop faster with radius than the mass distribution. This would correspond to a radially increasing total mass-to-light ratio. As velocity anisotropy alone cannot explain the observed kinematics in a simple a mass-follows-light model, we now allow for an mass-to-light ratio gradient in the JAM modelling to generate a mass model from the light distribution in Table \ref{tab:MGEF814W}. We do this by assigning each of the five Gaussians in the MGE its own mass-to-light ratio and replace the total luminosity in Eq. (\ref{eq:centralItotalL}) $L_i$ with the Gaussians total Mass $M_i = \Upsilon_{i} L_i$. We treat the five $\Upsilon_i$ as free parameters and only require that $\Upsilon_{j} \geq \Upsilon_i$ when the corresponding $\sigma_j \geq \sigma_i$ to ensure an overall mass-to-light ratio that is increasing with radius. [TO DO: Discuss Figure]

@@

\begin{figure*}
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[height=6cm]{fig/jam_G_vrms.ps}
  \caption{Comparison between the stellar $v_\text{rms}$ data (blue points) and the best fit JAM model using an increasing }
  \label{fig:JAM_modelG}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[height=6cm]{fig/jam_G_enclMass.ps}
  \caption{??? [TO DO: Make figure wider. Include legend.???] [TO DO: Why does this plot look different than the others???]}
  \label{fig:???}
\end{subfigure}
\caption{JAM model found by using an increasing mass-to-light ratio to generate a mass model from the light distribution in Table \ref{tab:MGEF814W}. [TO DO]??? Using the surface brightness MGE for the dynamical modelling: each Gaussian got it's own M/L such that the overall M/L is increasing with radius. This is the best fit model. The enclosed mass is overplotted with Einstein mass with 4\% error (overplotted, not fitted). ??? [TO DO: nice caption]}
\label{fig:???}
\end{figure*}
